simulation study in fjords

### 2024-04-11 R/simulation_study/simulation_study_fjords.Rmd
update simulation study

## Fix time steps for observations

@@

## Set observation error

@@

## Fix smooth parameters

@@

## Estimation when omega only is smooth

### Generate samples : high frequency and no measurement error

@@

## percentage of samples that reached land

@@

### Generate samples : low frequency and no measurement error

@@

### Generate samples : high frequency and measurement error

@@

```{r percentage of hf e samples that reached land}
count=0
for (id in unique(data_fjords_hf_e$ID)){
  sub_data=data_fjords_hf_e[data_fjords_hf_e$ID==id,]
  if (nrow(sub_data) < n_hf) {
    print(id)
    count=count+1
  }
}
cat(count/n_samples*100,"percent of the samples reached land")
```
### Plot samples

@@

### Generate samples : low frequency and measurement error

@@

### Compute distance to shore and empirical deviation angles

@@

### Estimate from high frequency data without error : ExpShore and tensor splines ti

@@

### Estimation from low frequency data without error

@@

### Estimate from high frequency data with error : ExpShore and tensor splines te

@@

### Estimate from low frequency data with error : ExpShore and tensor splines ti

>>>>

# Fix time steps for observations

@@

# Set observation error

@@

# Fix smooth parameters

@@

# Estimation when omega only is smooth

## Generate samples

### High frequency and no measurement error

@@

### percentage of samples that reached land

@@

### Low frequency and no measurement error

@@

### High frequency and measurement error

@@

```{r percentage of hf e samples that reached land}
count=0
for (id in unique(data_fjords_hf_e$ID)){
  sub_data=data_fjords_hf_e[data_fjords_hf_e$ID==id,]
  if (nrow(sub_data) < n_hf) {
    print(id)
    count=count+1
  }
}
cat(count/n_samples*100,"percent of the samples reached land")
```

@@

### Low frequency and measurement error

@@

## Compute distance to shore and empirical deviation angles

@@

## Estimations

### High frequency data without error : ExpShore and tensor splines ti

@@

### Low frequency data without error

@@

### High frequency data with error : ExpShore and tensor splines te

@@

### Low frequency data with error : ExpShore and tensor splines ti
